Edge sign prediction in general graphs and Correlation Clustering

### 2017-08-24 cc/cc_problem_and_esp.tex
elaborate on the connection between CC and ESP

\subsubsection{Connection with \esp{} and other applications}
\label{ssub:cc_applications}

According to \textcite[Section 5]{Demaine2006}, \pcc{} is well suited to several situations:
\begin{itemize}
   \item when the items to be clustered do not belong to a natural metric space (preventing
      approaches such as $k$-means) but we still know for some pairs whether they are similar or
      not.
   \item when we do not know the number of clusters beforehand but we have a similarity measure. In
      that case, we can select a problem-specific similarity threshold and set all edges with a
      similarity larger than the threshold to be positive while the others are set to negative.
   \item when we have a classic clustering problem (that is a set of objects, a distance between
      them and an objective function to minimize) with additional pairwise constraints of the form
      \emph{must-link/cannot-link}. Instead of restraining a clustering algorithm to the space of
      feasible solution, we convert the distances between objects and the constraints into signed
      edges and solve the resulting \pcc{} problem. 
\end{itemize}

In addition to these general considerations, \pcc{} has also been used in several domains:

>>>>

\paragraph{Connection with \esp{} and other applications}
\label{ssub:cc_applications}

\esp{} can clearly be casted as a supervised classification problem where, given a labelled training
set of $m_0$ edges $\mathcal{X}=\{(e_1, y_1), \ldots, (e_{m_0}, y_{m_0})\}$, we can extract for
every edge a feature vector in $\Rbb^d$, pick an hypothesis class like linear models, find among
this class the hypothesis minimizing the empirical risk, and use it to predict the sign of edges in
the testing set. In contrast, \pcc{} in an agnostic problem. More precisely, the hypothesis class is
fixed, as it consists of all possible partitions of the nodeset. We are trying to find the partition
that best approximates the observed signs, but each weakly unbalanced cycle is gonna cost us at
least one unavoidable mistakes. Despite this fundamental difference in their nature, \pcc{} is
connected with \esp{} at two levels, theoretical and practical. On the theoretical side, computing
the minimum number of disagreements gives a measure of the \esp{} problem complexity.  Intuitively,
given a labelled subgraph $H$ of $G$ (that is the training set), if there are few disagreements, the
\enquote{quasi} connected components of $H^+$ should give a reasonable estimation of the underlying
consistent clustering. Predicting the signs based on this clustering should results in few errors.
More formally, one can show that by finding a clustering $\cluster^\star$ of $H$ that has less
disagreements than $\kappa$ times the smallest number of disagreements $\Delta$, the number of
errors on the testing set will be at most of order $\kappa\Delta + \sqrt{mn\log
n}$~\autocite[Theorem 6]{Cesa-Bianchi2012b}. These theoretical considerations naturally lead to
practical batch algorithm, which first finds a clustering minimizing as much as possible the number
of disagreements on the training set and then predicts signs according to this clustering. Our
assumption in doing so is that, according to our bias, our graph has few disagreements. Therefore,
provided we can find a clustering close to the optimal, we will not make too many prediction
mistakes.

\bigskip

Besides the special case of predicting edge sign, \textcite[Section 5]{Demaine2006} point out that
\pcc{} is well suited to several more general situations:
\begin{itemize}
   \item when the items to be clustered do not belong to a natural metric space (preventing
      approaches such as $k$-means) but we still know for some pairs whether they are similar or
      not.
   \item when we do not know the number of clusters beforehand but we have a similarity measure. In
      that case, we can select a problem-specific similarity threshold and set all edges with a
      similarity larger than the threshold to be positive while the others are set to negative.
   \item when we have a classic clustering problem (that is a set of objects, a distance between
      them and an objective function to minimize) with additional pairwise constraints of the form
      \emph{must-link/cannot-link}. Instead of restraining a clustering algorithm to the space of
      feasible solution, we convert the distances between objects and the constraints into signed
      edges and solve the resulting \pcc{} problem. 
\end{itemize}

Furthermore, as mentioned in the introduction of this thesis, \pcc{} has also been used in several
domains. For instance in computer vision, it is used to segment images in
2D~\autocites{Kim2011}{Bagon2011}{CellSeg14} or 3D~\autocites{VolumeSegmentation12}{Beier2015}, to
simplify 3D shapes~\autocite{Shape3D17} and to track target across sequential video
frames~\autocite{multiTracking15}. When the nodes are words, \pcc{} is employed to identify
coreference~\autocites{graphicalCoreference04}{Elsner2009} or cluster synonym
words~\autocite{SignedWordRatings}. It plays a large role in biology, to clusters
genes~\autocite{Ben-Dor99}, identify mutation regions in chromosomes~\autocite{Das2015} or finding
stable subsystems~\autocite{monotoneBiology07}. Applied to social networks, it helps analyze
political assemblies~\autocites{Mendonca2015}{Jiang2015}{BrazilCC17} and international
relations~\autocites{Traag2009}{CommunityUN12}. Finally, given large databases with duplicated
records, it naturally models entity
resolution~\autocites{Crosslingual07}{DeDup09}{LargeScaleDeDup09}{WeightedER14}.
